---
title: "Home Work One"
format:
  revealjs: 
    theme: sky
    slide-number: true
    scrollable: true
    fontsize: 1.4em
    embed-resources: false
    standalone: false

---

```{r}
#| label: Importing-Data
#| echo: false
#| message: false
#| warning: false
# Libraries
library(ggplot2)
library(tidyverse)

# Loading the datasets
data(ChickWeight)
df = ChickWeight
```

### Data Description

The data set **ChickWeight** was originally part of the package *nlme*   
and has measurements of the body weights of chicks     
that were fed with different types of diets.    
The data set has `r dim(df)[1]` rows and `r dim(df)[2]` columns.    
The features are :   

 + <span style="color: red;">weight</span>

 + <span style="color: yellow;">Time</span>

 +  <span style="color: blue;">Chick</span>

 +  <span style="color: green;">Diet</span>

 
***

### Weight Distibution

According to the help [file](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/ChickWeight) of this dataset       
the body weights of the chicks were recorded every second     
day from their birth until the 21st day.    
The graph below shows the distribution of the chick weights.     
The <span style="color: black;">black dashed line</span> shows the mean weight which is `r round(mean(df$weight), digits = 2)` gm.     
We see that the mode is around 50 gm.    

```{r}
#| label: Weight-Distribution
#| echo: false
#| message: false
#| warning: false
#| fig-width: 20
#| fig-height: 15

# distribution of weight
ggplot(df, aes(x = weight)) +
  geom_density(fill = "blue", alpha = 0.3) + 
  geom_vline(aes(xintercept = mean(weight)),
             color = "black",linetype = "dashed",
             size = 0.5) +
  theme_linedraw() +
  labs(title = "Distribution of Chick Weights", x = "Weight", y = "Density")
```

***

### Data Summary

Below is a summary of each feature.

```{r}
#| label: Data-Statistics
#| echo: false
#| message: false
#| warning: false

# Displaying stats of each column
summary(df)
```

From the output above we see that the minimum weight is 35 gm   
and the max is 373 gm. We see for the time variable the max day is 21.   
The measurements started on day 0 and ended on day 21.   
The feature *Chick* is a unique identifier and an ordered factor.   
Here the summary shows the chicks with the most frequent count of observations.    
The variable Diet is also a categorical variable and it shows   
the amount of observations per category.

***

### Box Plots

```{r}
#| label: Box-Plots
#| echo: false
#| message: false
#| warning: false
#| fig-width: 20
#| fig-height: 15

# Changing diet into a factor
df$Diet = factor(df$Diet)

# Boxplots of weights per diet types
ggplot(df, aes(x = Diet,y = weight, fill = Diet)) +
  geom_boxplot() +
  theme_light() +
  labs(title = "Weight of Chicks ~ Diet", x = "Diet Type", y= "Weight")
```

The plot above illustrates the distribution of the      
chick weights for each diet type. Diet 4 seems to have        
the highest median weight and diet 1 the lowest median.    
We see that there might be a significant difference in means for each diet.   
In order to test this we could perform an anova test to see         
if there is a significant difference in means.      

***

# Assignment Two
### Creating two changes to commit to the github repository

```{r}
#| label: Change-One
#| echo: false
#| message: false
#| warning: false
#| fig-width: 20
#| fig-height: 15

ggplot(df, aes(x = Time, y = weight, color = Diet)) +
  geom_point() +
  theme_light() +
  labs(title = "Time ~ Weight")

```

```{r}
#| label: Change-Two
#| echo: false
#| message: false
#| warning: false
#| fig-width: 20
#| fig-height: 15

ggplot(df, aes(x = Chick, y = weight, fill = Chick)) +
  geom_boxplot() +
  theme_light() +
  labs(title = "Distribution of each Chicks Weight") +
  theme(legend.position = "none")

```

